Biogeography of crop progenitors and wild plant resources in the terminal Pleistocene and Early Holocene of West Asia, 14.7–8.3 ka

### 2025-03-31 analysis/paper.qmd
Add lay summary

<!--

* [x] Stop modelling
- [x] First draft:
- [x] Figures
- [ ] Biogeography background section
- [ ] Revise discussion of archaeo verification
- [ ] Outstanding TODOs
- [ ] Add missing references
- [ ] Copyedit
- [x] Appendix with all hindcast predictions (HTML?)
- [ ] Clean up package code
- [ ] Zenodo release
- [ ] Final proofread

-->

>>>>

<!--
TODO before publication:
- [ ] Revise discussion of archaeo verification
- [ ] Outstanding TODOs
- [ ] Add missing references
- [x] Appendix with all hindcast predictions (HTML?)
- [ ] Clean up package code
- [ ] Zenodo release
- [ ] Final proofread
-->
